Peaks Over Threshold for Bursty Time Series

### 2018-05-08 article_springer/index.Rmd
manually add authors, keywords & grant

---
title: "Peaks Over Threshold for Bursty Time Series"
# titlerunning: "CTRE: POT for Bursty Time Series"
thanks: |
    Peter Straka was supported by the 
    Discovery Early Career Research Award DE160101147 on the Project 
    "Predicting Extremes when Events Occur in Bursts" by the Australian
    Research Council.
    Katharina Hees was supported by 
    the DAAD co-financed by the German Federal Ministry of Education and 
    Research (BMBF). 
authors:

- name: "Katharina Hees"
  address: University of Dortmund
  email: hees@statistik.uni-dortmund.de
- name: "Smarak Nayak"
  address: National Australia Bank
  email: smarak.nayak@nab.com.au
- name: "Peter Straka*"
  address: UNSW Sydney
  email: p.straka@unsw.edu.au 
authorrunning: K. Hees, S. Nayak & P. Straka
keywords:
- heavy tails
- renewal process
- extreme value theory
- peaks over threshold
abstract: |
  In many complex systems studied in statistical physics, 
  inter-arrival times between events such as solar flares, trades and 
  neuron voltages follow a heavy-tailed 
  distribution. The set of event times is fractal-like, being dense in some 
  time windows and empty in others, a phenomenon which has been dubbed 
  "bursty".

@@

>>>>

---
title: "Peaks Over Threshold for Bursty Time Series"
# titlerunning: "CTRE: POT for Bursty Time Series"
thanks: |
    Peter Straka was supported by the 
    Discovery Early Career Research Award DE160101147 on the Project 
    "Predicting Extremes when Events Occur in Bursts" by the Australian
    Research Council.
    Katharina Hees was supported by 
    the DAAD co-financed by the German Federal Ministry of Education and 
    Research (BMBF). 
author: 
  - Katharina Hees, TU Dortmund
  - Smarak Nayak, National Australia Bank
  - Peter Straka, UNSW Sydney

authors:

- name: "Katharina Hees"
  address: TU Dortmund
  email: hees@statistik.uni-dortmund.de
- name: "Smarak Nayak"
  address: National Australia Bank
  email: smarak.nayak@nab.com.au
- name: "Peter Straka*"
  address: UNSW Sydney
  email: p.straka@unsw.edu.au 
authorrunning: K. Hees, S. Nayak & P. Straka
keywords:
- heavy tails
- renewal process
- extreme value theory
- peaks over threshold
abstract: |
  In many complex systems studied in statistical physics, 
  inter-arrival times between events such as solar flares, trades and 
  neuron voltages follow a heavy-tailed 
  distribution. The set of event times is fractal-like, being dense in some 
  time windows and empty in others, a phenomenon which has been dubbed 
  "bursty".

@@

Keywords:

: _heavy tails, renewal process, extreme value theory, peaks over threshold_

Thanks:

: * Peter Straka was supported by the 
Discovery Early Career Research Award DE160101147 on the Project 
"Predicting Extremes when Events Occur in Bursts" by the Australian
Research Council.
* Katharina Hees was supported by 
the DAAD co-financed by the German Federal Ministry of Education and 
Research (BMBF).
